Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions

### 2010-11-05 rjournal/RJtemplate.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@20 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[article]{jss}

\usepackage{amsthm, amsmath, amssymb}
%\usepackage{Sweave}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% almost as usual
\author{Taylor B. Arnold \\ Yale University \And 
        John W. Emerson\\ Yale University}
\title{Nonparametric Goodness-of-Fit Tests \\ for Discrete Null Distributions}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Taylor B. Arnold, John W. Emerson} %% comma-separated
\Plaintitle{Nonparametric Goodness-of-Fit Tests for Discrete Distributions} %% without formatting
\Shorttitle{Nonparametric Goodness-of-Fit Tests for Discrete Distributions} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
   A general theory for extending nonparametric goodness-of-fit tests to discrete null distributions has existed
   for several decades. Despite this, modern statistical software have generally failed to provide this methodology
   to users. The packages \pkg{ks.test} and \pkg{cvm.test} serve to fill this need in the \proglang{R} language for
   the two most popular nonparametric tests. The structure of these two packages are explained and examples
   to their specific usage are presented. Particular attention is given to the various numerical issues that arise
   in their implementation.

*** try to clean up, avoid package/function issue, make it a general
contribution if possible.
}
\Keywords{Cramer von Mises, goodness-of-fit tests, Kolmogorov-Smirnov, \proglang{R}}
\Plainkeywords{Cramer von Mises, goodness-of-fit tests, Kolmogorov-Smirnov, R} %% without formatting
%% at least one keyword must be supplied

%% publication information
%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
%% \Volume{13}
%% \Issue{9}
%% \Month{September}
%% \Year{2004}
%% \Submitdate{2004-09-29}
%% \Acceptdate{2004-09-29}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Taylor B. Arnold \\
  24 Hillhouse Ave. \\
  New Haven, CT 06511, USA\\
  E-mail: \email{taylor.arnold@yale.edu}\\
  URL: \url{http://euler.stat.yale.edu/~tba3}\\

  John W. Emerson \\
  24 Hillhouse Ave. \\
  New Haven, CT 06511, USA\\
  E-mail: \email{john.emerson@yale.edu}\\
  URL: \url{http://euler.stat.yale.edu/~jay}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/1/31336-5053
%% Fax: +43/1/31336-734

%% for those who use Sweave please include the following line (with % symbols):
%% need no \usepackage{Sweave.sty}

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\setkeys{Gin}{width=1.0\textwidth, height=1.0\textheight}

%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

@@

Example code:
\begin{Schunk}
\begin{Sinput}
> 1 + 1
\end{Sinput}
\begin{Soutput}
[1] 2
\end{Soutput}
\end{Schunk}

@@

%Why we use non-parametric tests (power to interesting shifts; robustness to underlying assumptions).
While almost any hypothesis test can be viewed as a variant on a goodness-of-fit test, the term is typically
applied to those tests which are nonparametric in nature. That is, they do not conduct the hypothesis testing 
through the explicit calculation of the parameters generating the data. Instead, they generally attempt to 
calculate differences between the empirical distribution of the observed data and the overall distribution 
of the null model. In many cases these tests are preferential since they tend to have an increased power for 
interesting deviations from the null model, in exchange for failing to detect less interesting deviations due to 
factors such as measurement error. By far the most popular of these nonparametric tests are due to Kolmogorov and 
Smirnov, followed closely by several variants on an estimation procedure proposed by Cramer von Mises.

% Discrete versions exist; just no code
While the original aim of nonparametric goodness of fit tests was meant for continuous null distributions, discrete versions
have existed since the early 1970s. Unfortunately, current statistical software has largely failed to incorporate them.
This has left the end-user to either use only parametric tests, such as Pearson's Chi-Squared test, or to incorrectly
apply the functions meant for continuous distributions. As shown in section 5, the latter can be particularly dangerous
in the small sample setting. The packages \pkg{ks.test} and \pkg{cvm.test} serve to fill this void for users
operating in the \proglang{R} environment.

@@

Of all the methods for nonparametric goodness-of-fit tests, by far the most popular is the method devised by Kolmogorov and Smirnov.
It is the only such test built into the base of \proglang{R}. The idea behind it is fairly simple. Given the cumulative distribution
function $F_0(x)$ of the continuous null distribution, and the empirical distribution function $F_{data}(x)$ of the observed data, 
one constructs the statistic:
\begin{align}
D = \sup_x \left| F_0(x)- F_{data}(x) \right|
\end{align}
The distribution of $D$ under the null model does not depend on which null distribution is being used, making this a computationally
attractive method. For a standard treatment of the test and its performance relative to other algorithms see \cite{slakter65}. Two common
alternatives of the above test statistic exist. The absolute value is discarded and the rest is either left alone (the `greater' testing 
alternative) or the supremum is replaces with a negative infimum (the `lesser' hypothesis alternative). These can be helpful depending 
on the nature of the alternative hypotheses for which the test is desired to be powerful towards.

@@

\begin{align}
\sup_x \left| f(x)- g(x) \right| &= \max_i \left( \left|g(x_i) - f(x_i) \right|, \lim_{x \rightarrow x_i} \left| g(x) - f(x_{i-1}) \right| \right) \\
&=  \max_i \left( \left|g(x_i) - f(x_i) \right|, \left| g(x_i) - f(x_{i-1}) \right| \right)
\end{align}

Computing the maximum over these $2N$ values (with $f$ equal to $F_{data}(x)$ and $g$ equal to $F_0(x)$ as defined above) is clearly the 
most efficient way to compute the Kolmogorov-Smirnov test statistic when given a continuous null distribution. When the function $g$ is not
continuous, notice that this formula no longer works since in general we cannot replace the limit of $g$ with its value at $x_i$. If it is known that $g$
is also a step function, we could replace the formula for some small $\epsilon$ by:
\begin{align}
\sup_x \left| f(x)- g(x) \right| &=  \max_i \left( \left|g(x_i) - f(x_i) \right|, \left| g(x_i - \epsilon) - f(x_{i-1}) \right| \right)
\end{align}
Where the discontinuities in $g$ are at least a distance $\epsilon$ apart. But this requires knowing that $g$ is a step function. In the case of not knowing,
or having a $g$ which is in neither a step function nor a continuous function, the only method for computing the supremum is to take the numerical limit in (1). 
This clearly takes more computational time than simply cycling over $2N$ values.

@@

%Once the test statistic is determined, the p-value for this value needs to be computed. For high sample sizes, the test distribution becomes the same as in the
%continuous case. The default options for \pkg{ks.test} already allow the user to specify if they would like approximate asymptotic distributions (since these exist
%in the continuous setting as well). So when this approximation flag is turned on, this distribution is used for all situations. When the user requires exact p-values,
%the methodology in \citet{Conover1972} needs to be used. Code for this procedure in the \proglang{R} language, or in any other open source options, did not previously
%exist and is included in the revised \pkg{ks.test}. The calculations are complex but straightforward; the full details are contained in the package source and in 
%the original Conover paper.

@@

*** Check Cramer-von Mises for hyphen, and let's get the accent done properly.

\section{Cramer von Mises Tests}

@@

%General idea for continuous distributions. In many cases actually more powerful of the two. There again exists a distribution free 
%distribution for the testing statistic.
While the Kolmogorov-Smirnov test is the most well known of the non-parametric goodness of fit tests, there is another family of 
tests which has been shown to be more powerful to a large class of alternatives distributions. The original was developed jointly by
Harald Cramer and Richard von Mises \citep{cramer1928, vonmises1928}, and further adapted by \cite{anderson1952}, and 
\cite{Watson1961}. The test statistics are, respectively, given as:
\begin{align*}
W^2 &= n \cdot \int_{-\infty}^{\infty} \left[ F_{data}(x)- F_{0}(x) \right]^2 dF_0(x) \\
A^2 &= n \cdot \int_{-\infty}^{\infty} \left[F_0(x) -F_0(x)^2 \right]^{-1} \left[ F_{data}(x)- F_{0}(x) \right]^2 dF_0(x) \\
U^2 &= n \cdot \int_{-\infty}^{\infty} \left[ F_{data}(x)- F_{0}(x) - W^2 \right]^2 dF_0(x)
\end{align*}
Where $F$ is either the cumulative distribution of the null model or the empirical cumulative distribution of the observed data.
As in the Kolmogorov-Smirnov test statistic, these all have distribution free null distributions in the continuous case.

@@

%Discuss the discrete version. How to calculate W2, U2, and A2. 
Generalizations of the Cramer-von Mises tests were developed in \cite{choulakian1994}. Much like for the Kolmogorov-Smirnov test,
the theoretical form of the test statistics are unchanged; although the discreteness allows for a slightly simpler representation.
The null distribution of the test statistics are again distribution dependent, unlike the continuous version. The methods do not
suggest finite sample results, but rather show that the asymptotic null distribution is equal to a weighted sum of independent
chi-squared variables (the weights depending on the particular distribution). This asymptotic distribution is what we implement here;
the original papers shows that this approximation (*** NOT FINISHED?)

@@

There is no analytic solution to the integral, but integration can be carried out using numerical techniques. This seems
fine in most situations, but numerical issues do become a problem in the regime of large test statistics $x$. The function
$\theta(\cdot, x)$ is linear in $x$, and thus as the the test statistic grows the corresponding period of the integrand 
decreases. As the function acquires too many inflection points, the approximation becomes unstable. This is further
magnified by this occurring when $p$-values should be very small; thus tiny fluctuations which would be undetectable
elsewhere are quite prominent. Figure ? shows the non-monotonicity of the function as the test statistic grows.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kolmogorov-Smirnov and Cramer von Mises Tests in R}

Package \pkg{ks.test} contains function \code{ks.test()}, a revision of
\proglang{R}'s Kolmogorov-Smirnov function \code{ks.test()} from base
package \pkg{stats}.
Package \pkg{cvm.test} contains function \code{cvm.test()}, a new
function for Cramer von Mises tests.  Both are available from the authors
as of October, 2010,
or from R-Forge (\url{https://r-forge.r-project.org/R/?group_id=802});
they will be proposed for inclusion in \pkg{stats} in late 2010.

The revised \pkg{ks.test()} function supports one-sample tests for discrete
null distributions by allowing the second argument, \code{y}, to be
an empirical cumulative distribution function (an \proglang{R} function
with class \code{ecdf}) or an object of class \code{stepfun} specifying
a discrete distribution.  As in the original version of \code{ks.test()},
the presence of ties in the data (the first argument, \code{x}) generates a
warning unless \code{y} describes a discrete distribution.  When a discrete
distribution is specified, exact p-values are not available for 
two-sided alternative hypotheses, but the reported p-values will be
conservative.  For one-sided tests,
exact p-values are calculated using Conover's
method (when \code{exact = NULL} or \code{exact = TRUE})
if the sample size is less than or equal to 30; otherwise, asymptotic distributions
are used which are reliable in such cases (CITATION? Is this correct?).
When \code{exact = FALSE} the asymptotic distribution is used which is known
to be imprecise but conservative, even for small sample (CITATION).

@@

The function \pkg{cvm.test()} is similar to \pkg{ks.test()}.  Its first two
arguments specify the data and null distribution; the only extra option,
\code{type}, specifies the variant of the Cramer-von Mises test:
\begin{itemize}
\item \code{x}: a numerical vector of data values.
\item \code{y}: an \code{ecdf} or step-function (\code{stepfun}) for specifying
the null model
\item \code{type}: the variant of the Cramer-von Mises test; \code{W2}
is the default and most common method, \code{U2} is for cyclical data,
and \code{A2} is the Anderson-Darling alternative.
\end{itemize}
As with \code{ks.test()}, \code{cvm.test()} returns an object of class 
\code{htest}.

@@

\begin{Schunk}
\begin{Sinput}
set.seed(1)
REPS <- 100000
asymp.pval <- rep(0, REPS)
exact.pval <- rep(0, REPS)
for (i in 1:REPS) {
  x <- sample(1:10, 15, replace=TRUE)
  asymp.pval[i] <- stats::ks.test(x, ecdf(1:10), alternative="g")$p.value
  exact.pval[i] <- ks.test::ks.test(x, ecdf(1:10), alternative="g")$p.value
}
sum(asymp.pval<exact.pval)/REPS
sum(asymp.pval<=0.05)/REPS
sum(exact.pval<=0.05)/REPS
sqrt(0.05*0.95/REPS)
\end{Sinput}
\end{Schunk}

\begin{verbatim}
#####################################################
# 100000:

> sum(asymp.pval<exact.pval)/REPS
[1] 0
> sum(asymp.pval<=0.05)/REPS
[1] 0.01848
> sum(exact.pval<=0.05)/REPS
[1] 0.03763
> 
> sqrt(0.05*0.95/REPS)
[1] 0.0006892024
> 
> REPS
[1] 1e+05
\end{verbatim}

@@

Benefits and drawbacks of using simulation to gather p-values. (*)

@@

*** Bibliography needs cleaning before we finish up, just don't forget.

%\bibliographystyle{plain}
\bibliography{jss}

\end{document}

>>>>

\title{Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions}
\author{by Taylor B. Arnold and John W. Emerson}

\maketitle

\abstract{
   A general theory for extending nonparametric goodness-of-fit tests to discrete null distributions has existed
   for several decades. Despite this, modern statistical software have generally failed to provide this methodology
   to users. The packages ks.test and cvm.test serve to fill this need in the R language for
   the two most popular nonparametric tests. The structure of these two packages are explained and examples
   to their specific usage are presented. Particular attention is given to the various numerical issues that arise
   in their implementation.

*** try to clean up, avoid package/function issue, make it a general
contribution if possible.
}

@@

@@

%Why we use non-parametric tests (power to interesting shifts; robustness to underlying assumptions).
While almost any hypothesis test can be viewed as a variant on a goodness-of-fit test, the term is typically
applied to those tests which are nonparametric in nature. That is, they do not conduct the hypothesis testing 
through the explicit calculation of the parameters generating the data. Instead, they generally attempt to 
calculate differences between the empirical distribution of the observed data and the overall distribution 
of the null model. In many cases these tests are preferential since they tend to have an increased power for 
interesting deviations from the null model, in exchange for failing to detect less interesting deviations due to 
factors such as measurement error. By far the most popular of these nonparametric tests are due to Kolmogorov and 
Smirnov, followed closely by several variants on an estimation procedure proposed by Cram\'{e}r-von Mises.

% Discrete versions exist; just no code
While the original aim of nonparametric goodness of fit tests was meant for continuous null distributions, discrete versions
have existed since the early 1970s. Unfortunately, current statistical software has largely failed to incorporate them.
This has left the end-user to either use only parametric tests, such as Pearson's Chi-Squared test, or to incorrectly
apply the functions meant for continuous distributions. As shown in section 5, the latter can be particularly dangerous
in the small sample setting. The packages \pkg{ks.test} and \pkg{cvm.test} serve to fill this void for users
operating in the R environment.

@@

Of all the methods for nonparametric goodness-of-fit tests, by far the most popular is the method devised by Kolmogorov and Smirnov.
It is the only such test built into the base of R. The idea behind it is fairly simple. Given the cumulative distribution
function $F_0(x)$ of the continuous null distribution, and the empirical distribution function $F_{data}(x)$ of the observed data, 
one constructs the statistic:
\begin{align}
D = \sup_x \left| F_0(x)- F_{data}(x) \right|
\end{align}
The distribution of $D$ under the null model does not depend on which null distribution is being used, making this a computationally
attractive method. For a standard treatment of the test and its performance relative to other algorithms see \cite{slakter65}. Two common
alternatives of the above test statistic exist. The absolute value is discarded and the rest is either left alone (the `greater' testing 
alternative) or the supremum is replaces with a negative infimum (the `lesser' hypothesis alternative). These can be helpful depending 
on the nature of the alternative hypotheses for which the test is desired to be powerful towards.

@@

\begin{align*}
\sup_x &\left| f(x)- g(x) \right|   \\
       &= \max_i \left( \left|g(x_i) - f(x_i) \right|, \lim_{x \rightarrow x_i} \left| g(x) - f(x_{i-1}) \right| \right) \\
&=  \max_i \bigg( \left|g(x_i) - f(x_i) \right|, \left| g(x_i) - f(x_{i-1}) \right| \bigg)
\end{align*}

Computing the maximum over these $2N$ values (with $f$ equal to $F_{data}(x)$ and $g$ equal to $F_0(x)$ as defined above) is clearly the 
most efficient way to compute the Kolmogorov-Smirnov test statistic when given a continuous null distribution. When the function $g$ is not
continuous, notice that this formula no longer works since in general we cannot replace the limit of $g$ with its value at $x_i$. If it is known that $g$
is also a step function, we could replace the formula for some small $\epsilon$ by:
\begin{align*}
\sup_x &\left| f(x)- g(x) \right| =   \\
        &                    \max_i \{ \left|g(x_i) - f(x_i) \right|, \left| g(x_i - \epsilon) - f(x_{i-1}) \right| \}
\end{align*}
Where the discontinuities in $g$ are at least a distance $\epsilon$ apart. But this requires knowing that $g$ is a step function. In the case of not knowing,
or having a $g$ which is in neither a step function nor a continuous function, the only method for computing the supremum is to take the numerical limit in (1). 
This clearly takes more computational time than simply cycling over $2N$ values.

@@

%Once the test statistic is determined, the p-value for this value needs to be computed. For high sample sizes, the test distribution becomes the same as in the
%continuous case. The default options for \pkg{ks.test} already allow the user to specify if they would like approximate asymptotic distributions (since these exist
%in the continuous setting as well). So when this approximation flag is turned on, this distribution is used for all situations. When the user requires exact p-values,
%the methodology in \citet{Conover1972} needs to be used. Code for this procedure in the R language, or in any other open source options, did not previously
%exist and is included in the revised \pkg{ks.test}. The calculations are complex but straightforward; the full details are contained in the package source and in 
%the original Conover paper.

@@

*** Check Cram\'{e}r-von Mises for hyphen, and let's get the accent done properly.

\section{Cram\'{e}r-von Mises Tests}

@@

%General idea for continuous distributions. In many cases actually more powerful of the two. There again exists a distribution free 
%distribution for the testing statistic.
While the Kolmogorov-Smirnov test is the most well known of the non-parametric goodness of fit tests, there is another family of 
tests which has been shown to be more powerful to a large class of alternatives distributions. The original was developed jointly by
Harald Cram\'{e}r and Richard von Mises \citep{cramer1928, vonmises1928}, and further adapted by \cite{anderson1952}, and 
\cite{Watson1961}. The test statistics are, respectively, given as:
\begin{align*}
W^2 &= n \cdot \int_{-\infty}^{\infty} \left[ F_{data}(x)- F_{0}(x) \right]^2 dF_0(x) \\
A^2 &= n \cdot \int_{-\infty}^{\infty} \frac{\left[F_{data}(x)- F_{0}(x) \right]^2}{F_0(x) -F_0(x)^2} dF_0(x) \\
U^2 &= n \cdot \int_{-\infty}^{\infty} \left[ F_{data}(x)- F_{0}(x) - W^2 \right]^2 dF_0(x)
\end{align*}
Where $F$ is either the cumulative distribution of the null model or the empirical cumulative distribution of the observed data.
As in the Kolmogorov-Smirnov test statistic, these all have distribution free null distributions in the continuous case.

@@

%Discuss the discrete version. How to calculate W2, U2, and A2. 
Generalizations of the Cram\'{e}r-von Mises tests were developed in \cite{choulakian1994}. Much like for the Kolmogorov-Smirnov test,
the theoretical form of the test statistics are unchanged; although the discreteness allows for a slightly simpler representation.
The null distribution of the test statistics are again distribution dependent, unlike the continuous version. The methods do not
suggest finite sample results, but rather show that the asymptotic null distribution is equal to a weighted sum of independent
chi-squared variables (the weights depending on the particular distribution). This asymptotic distribution is what we implement here;
the original papers shows that this approximation (*** NOT FINISHED?)

@@

There is no analytic solution to the integral, but integration can be carried out using numerical techniques. This seems
fine in most situations, but numerical issues do become a problem in the regime of large test statistics $x$. The function
$\theta(\cdot, x)$ is linear in $x$, and thus as the the test statistic grows the corresponding period of the integrand 
decreases. As the function acquires too many inflection points, the approximation becomes unstable. This is further
magnified by this occurring when $p$-values should be very small; thus tiny fluctuations which would be undetectable
elsewhere are quite prominent. Figure \ref{cvmissues} shows the non-monotonicity of the function as the test statistic grows.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{fig1.pdf}
\end{center}
\caption{Plot of p-value for given test statistics using numerical integration (pink) versus a conservative
         chi-squared bound (blue). }
\label{cvmissues}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kolmogorov-Smirnov and Cram\'{e}r-von Mises Tests in R}

Package \pkg{ks.test} contains function \code{ks.test()}, a revision of
R's Kolmogorov-Smirnov function \code{ks.test()} from base
package \pkg{stats}.
Package \pkg{cvm.test} contains function \code{cvm.test()}, a new
function for Cram\'{e}r-von Mises tests.  Both are available from the authors
as of October, 2010,
or from R-Forge (\url{https://r-forge.r-project.org/R/?group_id=802});
they will be proposed for inclusion in \pkg{stats} in late 2010.

The revised \pkg{ks.test()} function supports one-sample tests for discrete
null distributions by allowing the second argument, \code{y}, to be
an empirical cumulative distribution function (an R function
with class \code{ecdf}) or an object of class \code{stepfun} specifying
a discrete distribution.  As in the original version of \code{ks.test()},
the presence of ties in the data (the first argument, \code{x}) generates a
warning unless \code{y} describes a discrete distribution.  When a discrete
distribution is specified, exact p-values are not available for 
two-sided alternative hypotheses, but the reported p-values will be
conservative.  For one-sided tests,
exact p-values are calculated using Conover's
method (when \code{exact = NULL} or \code{exact = TRUE})
if the sample size is less than or equal to 30; otherwise, asymptotic distributions
are used which are reliable in such cases (CITATION? Is this correct?).
When \code{exact = FALSE} the asymptotic distribution is used which is known
to be imprecise but conservative, even for small sample (CITATION).

@@

The function \pkg{cvm.test()} is similar to \pkg{ks.test()}.  Its first two
arguments specify the data and null distribution; the only extra option,
\code{type}, specifies the variant of the Cram\'{e}r-von Mises test:
\begin{itemize}
\item \code{x}: a numerical vector of data values.
\item \code{y}: an \code{ecdf} or step-function (\code{stepfun}) for specifying
the null model
\item \code{type}: the variant of the Cram\'{e}r-von Mises test; \code{W2}
is the default and most common method, \code{U2} is for cyclical data,
and \code{A2} is the Anderson-Darling alternative.
\end{itemize}
As with \code{ks.test()}, \code{cvm.test()} returns an object of class 
\code{htest}.

@@

@@

The computational capabilities of modern computers provide an alternative to using a complex formula to
calculate the p-value for a test statistic. By drawing random samples from the null distribution, in many
cases the p-values for a given statistic can be calculated accurately in a relatively short time span.
This can be quite useful in some cases, but using the exact formulas from our methodology has several
distinct advantages. First of all, if the function is called many times (say, within another simulation
study), the computational benefits of using a formula can quickly become substantial. There is also a greater need
for supervision in a simulation study, with the exact number of runs needed to reach convergence (or other 
similar threshold). Additionally, while
simulations are generally a well received accepted method, it is often important in applied data analysis
to be sure that the calculated $p$-values are not the result of a numerical oddity in a particular
run of a simulation.

In the end, for methods such as those presented in this paper where it is possible
there are enough positives to suggest that we attempt to implement exact $p$-value calculations. This does lead
to an interesting direction for future research in non-parametric goodness of fit tests: the methods presented
here were historically chosen because they could be shown to have fixed null distributions which could easily
calculated in an era without fast computers for carrying out permutation tests. It is quite possible that
variants without the property, which could be easily used today, have greater power to certain alternative 
distributions.

@@

%\bibliography{example}

\bibliography{paper}

\address{
  Taylor B. Arnold \\
  24 Hillhouse Ave. \\
  New Haven, CT 06511
  USA\\
}
\email{taylor.arnold@yale.edu}

\address{
  John W. Emerson \\
  24 Hillhouse Ave. \\
  New Haven, CT 06511
  USA\\
}
\email{john.emerson@yale.edu}
